Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations

### 2022-01-26 paper2.Rmd
FIRST DRAFT COMPLETE !!!!

# Abstract 
How do individuals perform information search, and what factors help them decide
which information search vehicle to utilize, such as interpersonal networks or
online tools, I investigate the above question using individual survey data of
934 Adults in the United States and find that X and Y. Furthermore, this paper
demonstrates that searching for a question online using a search engine or
social network was more common than traditional means of information gathering,
such as network activation (asking someone in their social network for
informational support). Using X and Y theory I predict that that few people will
activate their social network for informational support in my chosen case of
Covid-19 vaccinations because of the social cost of doing so but fail to find
evidence for this thesis. I also investigate which information channels are
associated with vaccinations against the virus and find that social networking
sites are associated with lower rates. I also find important ethnoracial
differences in information search vehicles utilization and vaccination
reception.

<!-- TODO this needs a lot of work but its a start -->
Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. In this paper, I aim to
uncover just how different various methods of information search are and begin a
line of research inquiry that investigates the factors associated with each vehicle. 
Finally, I also aimed to uncover how the different fountains of information and
information search vehicles hold real world consequences through their associations
with Covid-19 vaccination rates and intentions.

Keywords: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks,

>>>>

# Abstract 
Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory I investigate the factors associated
with each vehicle type when on information seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of `r nrow(rain)` Americans and their experience seeking out
information about the Covid-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the vehicles queried
in this survey are conceptually different and that the utilization of different
vehicles varies by demography and information sources. Finally, I find that
different fountains of information and information search vehicles hold real
world consequences through their associations with Covid-19 vaccination rates
and intentions, as information from a doctor increased the Covid-19 vaccination
uptake while receiving information from a Social Networking Site like Facebook
or Twitter was associated with lower odds of vaccination.

**Keywords**: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks, Social Support, Information & Communication Technologies
